Forecasting the 2024 U.S. Presidential Election: An Analysis of Battleground States

### 2024-11-04 paper/paper.qmd
fix rendering

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplotone

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplottwo

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplotone
#| #| fig-cap: 'Diagnostic plots for Model 3'

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dgplottwo
#| fig-cap: 'Diagnostic plots for Model 6'
